---
title: "One person per group"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyr)
require(data.table)
require(kableExtra)
library(ggplot2)
```


## Tables

### Group settings: 

+ 30 people, 30 groups with 1 people in every group. 

+ T = 30 & 50

+ Group errors are generated from normal distributions with mean 0, and $\sigma^2 = 0.5$ for every group.

+ Random slope are generated from normal distributions with mean 0, and $\sigma^2$ changing from 0 to 1 by 0.1 for every round of simulation.

+ Y is generated as follows : 


$$
Y_{it} = (-0.2 + \text{slope}_i + \beta_{11}^*S_{it}) \times (A_{it} -p_t(1|H_{it})) + 0.8 S_{it} + \text{group_err}_i +\text{err}_{it}
$$

```{r include=FALSE}
cpc = matrix(NA, nrow = 6, ncol = 11)
```



#### The variance for random slope is 0

```{r echo=FALSE}
load("~/MRT/one person per group/sim-0.RData")
all <- omit

all_3030_wc= subset(all, n ==30 & tmax == 30 & method == "Weighted and centered")

all_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & method == "Weighted and centered")

all_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

```{r include=FALSE}
cpc[,1] = all$cpc
```


#### The variance for random slope is 0.1


```{r echo=FALSE}
load("~/MRT/one person per group/sim-0.1.RData")
all <- omit

all_3030_wc= subset(all, n ==30 & tmax == 30 & method == "Weighted and centered")

all_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```



```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & method == "Weighted and centered")

all_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

```{r include=FALSE}
cpc[,2] = all$cpc
```


#### The variance for random slope is 0.2


```{r echo=FALSE}
load("~/MRT/one person per group/sim-0.2.RData")
all <- omit

all_3030_wc= subset(all, n ==30 & tmax == 30 & method == "Weighted and centered")

all_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```



```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & method == "Weighted and centered")

all_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

```{r include=FALSE}
cpc[,3] = all$cpc
```


#### The variance for random slope is 0.3


```{r echo=FALSE}
load("~/MRT/one person per group/sim-0.3.RData")
all <- omit

all_3030_wc= subset(all, n ==30 & tmax == 30 & method == "Weighted and centered")

all_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```



```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & method == "Weighted and centered")

all_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

```{r include=FALSE}
cpc[,4] = all$cpc
```



#### The variance for random slope is 0.4


```{r echo=FALSE}
load("~/MRT/one person per group/sim-0.4.RData")
all <- omit

all_3030_wc= subset(all, n ==30 & tmax == 30 & method == "Weighted and centered")

all_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```



```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & method == "Weighted and centered")

all_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

```{r include=FALSE}
cpc[,5] = all$cpc
```


#### The variance for random slope is 0.5


```{r echo=FALSE}
load("~/MRT/one person per group/sim-0.5.RData")
all <- omit

all_3030_wc= subset(all, n ==30 & tmax == 30 & method == "Weighted and centered")

all_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```



```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & method == "Weighted and centered")

all_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

```{r include=FALSE}
cpc[,6] = all$cpc
```


#### The variance for random slope is 0.6


```{r echo=FALSE}
load("~/MRT/one person per group/sim-0.6.RData")
all <- omit

all_3030_wc= subset(all, n ==30 & tmax == 30 & method == "Weighted and centered")

all_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```



```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & method == "Weighted and centered")

all_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

```{r include=FALSE}
cpc[,7] = all$cpc
```



#### The variance for random slope is 0.7


```{r echo=FALSE}
load("~/MRT/one person per group/sim-0.7.RData")
all <- omit

all_3030_wc= subset(all, n ==30 & tmax == 30 & method == "Weighted and centered")

all_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```



```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & method == "Weighted and centered")

all_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

```{r include=FALSE}
cpc[,8] = all$cpc
```


#### The variance for random slope is 0.8


```{r echo=FALSE}
load("~/MRT/one person per group/sim-0.8.RData")
all <- omit

all_3030_wc= subset(all, n ==30 & tmax == 30 & method == "Weighted and centered")

all_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```



```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & method == "Weighted and centered")

all_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r include=FALSE}
cpc[,9] = all$cpc
```



#### The variance for random slope is 0.9


```{r echo=FALSE}
load("~/MRT/one person per group/sim-0.9.RData")
all <- omit

all_3030_wc= subset(all, n ==30 & tmax == 30 & method == "Weighted and centered")

all_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & method == "Weighted and centered")

all_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

```{r include=FALSE}
cpc[,10] = all$cpc
```

#### The variance for random slope is 1


```{r echo=FALSE}
load("~/MRT/one person per group/sim-1.RData")
all <- omit

all_3030_wc= subset(all, n ==30 & tmax == 30 & method == "Weighted and centered")

all_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```



```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & method == "Weighted and centered")

all_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

```{r include=FALSE}
cpc[,11] = all$cpc
cpc= cbind(all[,c("level","n","tmax")],cpc)
```


## Plots

```{r echo=FALSE}
ggplot() +
  geom_line(mapping=aes(x=0:10/10, y = as.numeric(cpc[1,4:14]),color = "#FF9999"),size = 1)+ 
  geom_line(mapping=aes(x=0:10/10, y = as.numeric(cpc[3,4:14]),color = "#0072B2"),size = 1)+ 
  geom_line(mapping=aes(x=0:10/10, y = as.numeric(cpc[5,4:14]),color = "#3300CC"),size = 1)+ 
  scale_color_identity(name ="Degree of moderation by S_t",
                       breaks = c("#FF9999", "#0072B2", "#3300CC"), 
                       labels = c("0.2", "0.5", "0.8"), 
                       guide = "legend")+ 
  xlab("Random slope variance")+ ylab("coverage probability")+ ggtitle("n =30, T = 30")

```


```{r echo=FALSE}
ggplot() +
  geom_line(mapping=aes(x=0:10/10, y = as.numeric(cpc[2,4:14]),color = "#FF9999"),size = 1)+ 
  geom_line(mapping=aes(x=0:10/10, y = as.numeric(cpc[4,4:14]),color = "#0072B2"),size = 1)+ 
  geom_line(mapping=aes(x=0:10/10, y = as.numeric(cpc[6,4:14]),color = "#3300CC"),size = 1)+ 
  scale_color_identity(name ="Degree of moderation by S_t",
                       breaks = c("#FF9999", "#0072B2", "#3300CC"), 
                       labels = c("0.2", "0.5", "0.8"), 
                       guide = "legend")+ 
  xlab("Random slope variance")+ ylab("coverage probability")+ ggtitle("n =30, T = 50")

```

