---
title: "Plot/Table"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("~/MRT/sim-omit_mrt.RData")
indep <- omit

load("~/MRT/sim-omit-0.RData")
corgroup_0 <-omit
load("~/MRT/sim-omit-0.1.RData")
corgroup_0.1 <-omit
load("~/MRT/sim-omit-0.2.RData")
corgroup_0.2 <-omit
load("~/MRT/sim-omit-0.3.RData")
corgroup_0.3 <-omit
load("~/MRT/sim-omit-0.4.RData")
corgroup_0.4 <-omit
load("~/MRT/sim-omit-0.5.RData")
corgroup_0.5 <-omit
load("~/MRT/sim-omit-0.6.RData")
corgroup_0.6 <-omit
load("~/MRT/sim-omit-0.7.RData")
corgroup_0.7 <-omit

# load("~/MRT/sim-omit-0.8.RData")
# corgroup_0.8 <-omit

load("~/MRT/sim-omit-0.9.RData")
corgroup_0.9 <-omit
load("~/MRT/sim-omit-1.RData")
corgroup_1 <-omit

library(tidyr)
require(data.table)
require(kableExtra)
```


# Table

## n = 30 & T =30

#### Group error variance = 0

```{r echo=FALSE}
corgroup_3030_wc= subset(corgroup_0, n ==30 & tmax == 30 & method == "Weighted and centered")

corgroup_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```


#### Group error variance = 0.1

```{r echo=FALSE}
corgroup_3030_wc= subset(corgroup_0.1, n ==30 & tmax == 30 & method == "Weighted and centered")

corgroup_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.2

```{r echo=FALSE}
corgroup_3030_wc= subset(corgroup_0.2, n ==30 & tmax == 30 & method == "Weighted and centered")

corgroup_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.3

```{r echo=FALSE}
corgroup_3030_wc= subset(corgroup_0.3, n ==30 & tmax == 30 & method == "Weighted and centered")

corgroup_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```


#### Group error variance = 0.4

```{r echo=FALSE}
corgroup_3030_wc= subset(corgroup_0.4, n ==30 & tmax == 30 & method == "Weighted and centered")

corgroup_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.5

```{r echo=FALSE}
corgroup_3030_wc= subset(corgroup_0.5, n ==30 & tmax == 30 & method == "Weighted and centered")

corgroup_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.6

```{r echo=FALSE}
corgroup_3030_wc= subset(corgroup_0.6, n ==30 & tmax == 30 & method == "Weighted and centered")

corgroup_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.7

```{r echo=FALSE}
corgroup_3030_wc= subset(corgroup_0.7, n ==30 & tmax == 30 & method == "Weighted and centered")

corgroup_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.9

```{r echo=FALSE}
corgroup_3030_wc= subset(corgroup_0.9, n ==30 & tmax == 30 & method == "Weighted and centered")

corgroup_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 1

```{r echo=FALSE}
corgroup_3030_wc= subset(corgroup_1, n ==30 & tmax == 30 & method == "Weighted and centered")

corgroup_3030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```

## n = 30 & T = 50

#### Group error variance = 0

```{r echo=FALSE}
corgroup_3050_wc= subset(corgroup_0, n ==30 & tmax == 50 & method == "Weighted and centered")

corgroup_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.1

```{r echo=FALSE}
corgroup_3050_wc= subset(corgroup_0.1, n ==30 & tmax == 50 & method == "Weighted and centered")

corgroup_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.2

```{r echo=FALSE}
corgroup_3050_wc= subset(corgroup_0.2, n ==30 & tmax == 50 & method == "Weighted and centered")

corgroup_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.3

```{r echo=FALSE}
corgroup_3050_wc= subset(corgroup_0.3, n ==30 & tmax == 50 & method == "Weighted and centered")

corgroup_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.4

```{r echo=FALSE}
corgroup_3050_wc= subset(corgroup_0.4, n ==30 & tmax == 50 & method == "Weighted and centered")

corgroup_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.5

```{r echo=FALSE}
corgroup_3050_wc= subset(corgroup_0.5, n ==30 & tmax == 50 & method == "Weighted and centered")

corgroup_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.6

```{r echo=FALSE}
corgroup_3050_wc= subset(corgroup_0.6, n ==30 & tmax == 50 & method == "Weighted and centered")

corgroup_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.7

```{r echo=FALSE}
corgroup_3050_wc= subset(corgroup_0.7, n ==30 & tmax == 50 & method == "Weighted and centered")

corgroup_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.9

```{r echo=FALSE}
corgroup_3050_wc= subset(corgroup_0.9, n ==30 & tmax == 50 & method == "Weighted and centered")

corgroup_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 1

```{r echo=FALSE}
corgroup_3050_wc= subset(corgroup_1, n ==30 & tmax == 50 & method == "Weighted and centered")

corgroup_3050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with pairwise correlation (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```

## n = 120 & T =30

#### Group error variance = 0

```{r echo=FALSE}
corgroup_12030_wc= subset(corgroup_0, n ==120 & tmax == 30 & method == "Weighted and centered")

corgroup_12030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =30)", align = "c") %>%
  kable_styling("striped")
```


#### Group error variance = 0.1

```{r echo=FALSE}
corgroup_12030_wc= subset(corgroup_0.1, n ==120 & tmax == 30 & method == "Weighted and centered")

corgroup_12030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =30)", align = "c") %>%
  kable_styling("striped")
```


#### Group error variance = 0.2

```{r echo=FALSE}
corgroup_12030_wc= subset(corgroup_0.2, n ==120 & tmax == 30 & method == "Weighted and centered")

corgroup_12030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =30)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.3

```{r echo=FALSE}
corgroup_12030_wc= subset(corgroup_0.3, n ==120 & tmax == 30 & method == "Weighted and centered")

corgroup_12030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =30)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.4

```{r echo=FALSE}
corgroup_12030_wc= subset(corgroup_0.4, n ==120 & tmax == 30 & method == "Weighted and centered")

corgroup_12030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =30)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.5

```{r echo=FALSE}
corgroup_12030_wc= subset(corgroup_0.5, n ==120 & tmax == 30 & method == "Weighted and centered")

corgroup_12030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =30)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.6

```{r echo=FALSE}
corgroup_12030_wc= subset(corgroup_0.6, n ==120 & tmax == 30 & method == "Weighted and centered")

corgroup_12030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =30)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.7

```{r echo=FALSE}
corgroup_12030_wc= subset(corgroup_0.7, n ==120 & tmax == 30 & method == "Weighted and centered")

corgroup_12030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =30)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.9

```{r echo=FALSE}
corgroup_12030_wc= subset(corgroup_0.9, n ==120 & tmax == 30 & method == "Weighted and centered")

corgroup_12030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =30)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 1

```{r echo=FALSE}
corgroup_12030_wc= subset(corgroup_1, n ==120 & tmax == 30 & method == "Weighted and centered")

corgroup_12030_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =30)", align = "c") %>%
  kable_styling("striped")
```


## n = 120 & T =50

#### Group error variance = 0

```{r echo=FALSE}
corgroup_12050_wc= subset(corgroup_0, n ==120 & tmax == 50 & method == "Weighted and centered")

corgroup_12050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =50)", align = "c") %>%
  kable_styling("striped")
```


#### Group error variance = 0.1

```{r echo=FALSE}
corgroup_12050_wc= subset(corgroup_0.1, n ==120 & tmax == 50 & method == "Weighted and centered")

corgroup_12050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.2

```{r echo=FALSE}
corgroup_12050_wc= subset(corgroup_0.2, n ==120 & tmax == 50 & method == "Weighted and centered")

corgroup_12050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.3

```{r echo=FALSE}
corgroup_12050_wc= subset(corgroup_0.3, n ==120 & tmax == 50 & method == "Weighted and centered")

corgroup_12050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.4

```{r echo=FALSE}
corgroup_12050_wc= subset(corgroup_0.4, n ==120 & tmax == 50 & method == "Weighted and centered")

corgroup_12050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.5

```{r echo=FALSE}
corgroup_12050_wc= subset(corgroup_0.5, n ==120 & tmax == 50 & method == "Weighted and centered")

corgroup_12050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.6

```{r echo=FALSE}
corgroup_12050_wc= subset(corgroup_0.6, n ==120 & tmax == 50 & method == "Weighted and centered")

corgroup_12050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.7

```{r echo=FALSE}
corgroup_12050_wc= subset(corgroup_0.7, n ==120 & tmax == 50 & method == "Weighted and centered")

corgroup_12050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 0.9

```{r echo=FALSE}
corgroup_12050_wc= subset(corgroup_0.9, n ==120 & tmax == 50 & method == "Weighted and centered")

corgroup_12050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =50)", align = "c") %>%
  kable_styling("striped")
```

#### Group error variance = 1

```{r echo=FALSE}
corgroup_12050_wc= subset(corgroup_1, n ==120 & tmax == 50 & method == "Weighted and centered")

corgroup_12050_wc[,c("level","truth","est","sec","cpc","rmse")] %>% 
  kable(caption = "Weighted and centered with group correlation (n=120, T =50)", align = "c") %>%
  kable_styling("striped")
```


