---
title: "Bigger sample size"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyr)
require(data.table)
require(kableExtra)
```

### When group effects are not changing throughout the time (sanity check)

#### Group settings: 

+ 625 people, 25 groups with 25 people in every group. 

+ Baseline group effects (don't influence treatment effect estimation) follow **N(0,0.5)**, $b_gs$ follow **N(0,0.1)**.

+ T = 30 & 50

+ Y is generated as follows : 


$$
Y_{i(t+1)} = (-0.2 + b_g +  \beta_{11}^*S_{it}) \times (A_{it} -p_t(1|H_{it})) + 0.8 S_{it} + \text{group_err}_g +\text{err}_{it}
$$

#### Model


$$
\text{y ~ state + I(a - pn)} 
$$

#### CP

We tested how often the CIs of the coefficient of $\text{I(a - pn)}$ covering $(-0.2 + b_g)$ in different groups. And how often we fail to reject the true treatment effect is $\bar \beta = 1/G \sum_{g=1}^G \beta_1^{(g)}$ on the group level.


```{r echo=FALSE}
load("~/MRT/testing/bg2-sanity.RData")
all <- omit

all_62530_wc= subset(all, n ==625 & tmax == 30 & level == '$\\beta_{11}^* = 0.2$')

all_62530_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =30)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_62530_wc$estc)
sd =sqrt(sum(all_62530_wc$sd^2))/max(all_62530_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```


```{r echo=FALSE}
all_62530_wc= subset(all, n ==625 & tmax == 30 & level == '$\\beta_{11}^* = 0.5$')

all_62530_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =30)", align = "c") %>%
  kable_styling("striped")
```

```{r echo=FALSE}
point = mean(all_62530_wc$estc)
sd =sqrt(sum(all_62530_wc$sd^2))/max(all_62530_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_62530_wc= subset(all, n ==625 & tmax == 30 & level == '$\\beta_{11}^* = 0.8$')

all_62530_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =30)", align = "c") %>%
  kable_styling("striped")
```

```{r echo=FALSE}
point = mean(all_62530_wc$estc)
sd =sqrt(sum(all_62530_wc$sd^2))/max(all_62530_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_62550_wc= subset(all, n ==625 & tmax == 50 & level == '$\\beta_{11}^* = 0.2$')

all_62550_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_62550_wc$estc)
sd =sqrt(sum(all_62550_wc$sd^2))/max(all_62550_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_62550_wc= subset(all, n ==625 & tmax == 50 & level == '$\\beta_{11}^* = 0.5$')

all_62550_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_62550_wc$estc)
sd =sqrt(sum(all_62550_wc$sd^2))/max(all_62550_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_62550_wc= subset(all, n ==625 & tmax == 50 & level == '$\\beta_{11}^* = 0.8$')

all_62550_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_62550_wc$estc)
sd =sqrt(sum(all_62550_wc$sd^2))/max(all_62550_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```


### When group effects change throughout the time

+ Same as above

+ Y is generated as follows : 


$$
Y_{i(t+1)} = (-0.2 + b_g + b_{g,2} \times t + \beta_{11}^*S_{it}) \times (A_{it} -p_t(1|H_{it})) + 0.8 S_{it} + \text{group_err}_g +\text{err}_{it}
$$

#### Model


$$
\text{y ~ state + I(a - pn)} 
$$

#### CP  

We tested how often the CIs of the coefficient of $\text{I(a - pn)}$ covering $(-0.2 + b_g)$ in different groups. And how often we fail to reject the true treatment effect is $\bar \beta = 1/G \sum_{g=1}^G \beta_1^{(g)}$ on the group level.


```{r echo=FALSE}
load("~/MRT/testing/test-bg2-625.RData")
all <- omit

all_62530_wc= subset(all, n ==625 & tmax == 30 & level == '$\\beta_{11}^* = 0.2$')

all_62530_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =30)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_62530_wc$estc)
sd =sqrt(sum(all_62530_wc$sd^2))/max(all_62530_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```


```{r echo=FALSE}
all_62530_wc= subset(all, n ==625 & tmax == 30 & level == '$\\beta_{11}^* = 0.5$')

all_62530_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =30)", align = "c") %>%
  kable_styling("striped")
```

```{r echo=FALSE}
point = mean(all_62530_wc$estc)
sd =sqrt(sum(all_62530_wc$sd^2))/max(all_62530_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_62530_wc= subset(all, n ==625 & tmax == 30 & level == '$\\beta_{11}^* = 0.8$')

all_62530_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =30)", align = "c") %>%
  kable_styling("striped")
```

```{r echo=FALSE}
point = mean(all_62530_wc$estc)
sd =sqrt(sum(all_62530_wc$sd^2))/max(all_62530_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_62550_wc= subset(all, n ==625 & tmax == 50 & level == '$\\beta_{11}^* = 0.2$')

all_62550_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_62550_wc$estc)
sd =sqrt(sum(all_62550_wc$sd^2))/max(all_62550_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_62550_wc= subset(all, n ==625 & tmax == 50 & level == '$\\beta_{11}^* = 0.5$')

all_62550_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_62550_wc$estc)
sd =sqrt(sum(all_62550_wc$sd^2))/max(all_62550_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_62550_wc= subset(all, n ==625 & tmax == 50 & level == '$\\beta_{11}^* = 0.8$')

all_62550_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_62550_wc$estc)
sd =sqrt(sum(all_62550_wc$sd^2))/max(all_62550_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

### When group effects change throughout the time

+ Same as above

+ Y is generated as follows : 


$$
Y_{i(t+1)} = (-0.2 + b_g + b_{g,2} \times t + \beta_{11}^*S_{it}) \times (A_{it} -p_t(1|H_{it})) + 0.8 S_{it} + \text{group_err}_g +\text{err}_{it}
$$

#### Model

We take the time changing effect into consideration:

$$
\text{y ~ state + I(a - pn)} + \text{t} + \text{I(a - pn)}\times \text{t}
$$

#### CP  

We tested how often the CIs of the coefficient of $\text{I(a - pn)}$ covering $(-0.2 + b_g)$ in different groups. And how often we fail to reject the true treatment effect is $\bar \beta = 1/G \sum_{g=1}^G \beta_1^{(g)}$ on the group level.


```{r echo=FALSE}
load("~/MRT/testing/test-tbg2.RData")
all <- omit

all_62530_wc= subset(all, n ==625 & tmax == 30 & level == '$\\beta_{11}^* = 0.2$')

all_62530_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =30)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_62530_wc$estc)
sd =sqrt(sum(all_62530_wc$sd^2))/max(all_62530_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```


```{r echo=FALSE}
all_62530_wc= subset(all, n ==625 & tmax == 30 & level == '$\\beta_{11}^* = 0.5$')

all_62530_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =30)", align = "c") %>%
  kable_styling("striped")
```

```{r echo=FALSE}
point = mean(all_62530_wc$estc)
sd =sqrt(sum(all_62530_wc$sd^2))/max(all_62530_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_62530_wc= subset(all, n ==625 & tmax == 30 & level == '$\\beta_{11}^* = 0.8$')

all_62530_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =30)", align = "c") %>%
  kable_styling("striped")
```

```{r echo=FALSE}
point = mean(all_62530_wc$estc)
sd =sqrt(sum(all_62530_wc$sd^2))/max(all_62530_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_62550_wc= subset(all, n ==625 & tmax == 50 & level == '$\\beta_{11}^* = 0.2$')

all_62550_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_62550_wc$estc)
sd =sqrt(sum(all_62550_wc$sd^2))/max(all_62550_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_62550_wc= subset(all, n ==625 & tmax == 50 & level == '$\\beta_{11}^* = 0.5$')

all_62550_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_62550_wc$estc)
sd =sqrt(sum(all_62550_wc$sd^2))/max(all_62550_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_62550_wc= subset(all, n ==625 & tmax == 50 & level == '$\\beta_{11}^* = 0.8$')

all_62550_wc[,c("level","group","estc","sec","cpc","g_cp","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=625, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_62550_wc$estc)
sd =sqrt(sum(all_62550_wc$sd^2))/max(all_62550_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```
