---
title: "Average group effect testing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyr)
require(data.table)
require(kableExtra)
```

## Tables

### Group settings: 

+ 30 people, 6 groups with 5 people in every group. 

+ Baseline group effects (don't influence treatment effect estimation) follow **N(0,0.5)**, and group random treatment effects follow **N(0,0.1)**.

+ T = 30 & 50

### Model

I constructed a model which looks like: (Group_i is an indicator function indicating whether this person belongs to group i, which takes value from {0,1} )

$$
y ~ state + I(a - pn) * (Group_1 + Group_2+ Group_3+ Group_4+ Group_5), # no Group 6 indicator because of collinearity.
$$
If we define the coefficients of 

**I(a - pn) ;  Group_1: I(a - pn) ;  Group_2: I(a - pn) ;  Group_3: I(a - pn) ;  Group_4: I(a - pn) ;  Group_5: I(a - pn)** 

as 

$$
\beta_0 , \beta_1 , \beta_2 , \beta_3 , \beta_4 , \beta_5
$$

And the null hypothesis we are trying to test is: 

$$
(6 \beta_0 + \beta_1 + \beta_2 + \beta_3 + \beta_4 + \beta_5)/6 = 0
$$
which is equivalent to the mean effect among 6 groups is 0. 


### Simulation

##### Worth noticing, the point estimations we've had for past work are all estimated without weighting (weights are all equal to 1), and achieved good reuslts. However, here if we still use unweighting point estimation for our test hypothesis, it's very far off.


```{r echo=FALSE}
load("~/MRT/testing/test.RData")
all <- omit

all_3030_wc= subset(all, n ==30 & tmax == 30 & method == "Weighted and centered")

all_3030_wc[,c("level","est","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Unweighted with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```





```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & method == "Weighted and centered")

all_3050_wc[,c("level","est","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Unweighted with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```



##### Change it to weighted estimation 


```{r echo=FALSE}
load("~/MRT/testing/testc.RData")
all <- omit

all_3030_wc= subset(all, n ==30 & tmax == 30 & method == "Weighted and centered")

all_3030_wc[,c("level","est","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```





```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & method == "Weighted and centered")

all_3050_wc[,c("level","est","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```



##### Chnage the null hypothesis to test the true mean group effect:

The null hypothesis we are trying to test now is: 

$$
(6 \beta_0 + \beta_1 + \beta_2 + \beta_3 + \beta_4 + \beta_5)/6 = -0.2
$$

which is equivalent to the mean effect among 6 groups is **-0.2**. 


```{r echo=FALSE}
load("~/MRT/testing/test-0.2.RData")
all <- omit

all_3030_wc= subset(all, n ==30 & tmax == 30 & method == "Weighted and centered")

all_3030_wc[,c("level","est","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```





```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & method == "Weighted and centered")

all_3050_wc[,c("level","est","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```


##### Compared to estimating average treatment effect altogether across 6 groups:


```{r echo=FALSE}
load("~/MRT/testing/compare.RData")
all <- omit

all_3030_wc= subset(all, n ==30 & tmax == 30 & method == "Weighted and centered")

all_3030_wc[,c("level","est","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```





```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & method == "Weighted and centered")

all_3050_wc[,c("level","est","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```


