---
title: "Group effect is changing with time"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyr)
require(data.table)
require(kableExtra)
```

## Tables

### When the group effects remain constants throughout the time

#### Group settings: 

+ 100 people, 4 groups with 25 people in every group. 

+ Baseline group effects (don't influence treatment effect estimation) follow **N(0,0.5)**, and group random treatment effects follow **N(0,0.1)**.

+ T = 30 & 50

+ Y is generated as follows : 


$$
Y_{i(t+1)} = (-0.2 + b_g + \beta_{11}^*S_{it}) \times (A_{it} -p_t(1|H_{it})) + 0.8 S_{it} + \text{group_err}_g +\text{err}_{it}
$$

#### Model

I constructed a model which looks like: 

$$
\text{y ~ state + I(a - pn)} 
$$

#### CP  

We tested whether the CI of the coefficient of $\text{I(a - pn)}$ covers $(-0.2 + b_g)$ or not in different groups. 


```{r echo=FALSE}
load("~/MRT/testing/test-100.RData")
all <- omit

all_10030_wc= subset(all, n ==100 & tmax == 30 & level == '$\\beta_{11}^* = 0.2$')

all_10030_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=100, T =30)", align = "c") %>%
  kable_styling("striped")
```

```{r echo=FALSE}
point = mean(all_10030_wc$estc)
sd =sqrt(sum(all_10030_wc$sd^2))/max(all_10030_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_10030_wc= subset(all, n ==100 & tmax == 30 & level == '$\\beta_{11}^* = 0.5$')

all_10030_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=100, T =30)", align = "c") %>%
  kable_styling("striped")
```

```{r echo=FALSE}
point = mean(all_10030_wc$estc)
sd =sqrt(sum(all_10030_wc$sd^2))/max(all_10030_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```


```{r echo=FALSE}
all_10030_wc= subset(all, n ==100 & tmax == 30 & level == '$\\beta_{11}^* = 0.8$')

all_10030_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=100, T =30)", align = "c") %>%
  kable_styling("striped")
```

```{r echo=FALSE}
point = mean(all_10030_wc$estc)
sd =sqrt(sum(all_10030_wc$sd^2))/max(all_10030_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```



```{r echo=FALSE}
all_10050_wc= subset(all, n ==100 & tmax == 50 & level == '$\\beta_{11}^* = 0.2$')

all_10050_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=100, T =50)", align = "c") %>%
  kable_styling("striped")
```

```{r echo=FALSE}
point = mean(all_10050_wc$estc)
sd =sqrt(sum(all_10050_wc$sd^2))/max(all_10050_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_10050_wc= subset(all, n ==100 & tmax == 50 & level == '$\\beta_{11}^* = 0.5$')

all_10050_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=100, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_10050_wc$estc)
sd =sqrt(sum(all_10050_wc$sd^2))/max(all_10050_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_10050_wc= subset(all, n ==100 & tmax == 50 & level == '$\\beta_{11}^* = 0.8$')

all_10050_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=100, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_10050_wc$estc)
sd =sqrt(sum(all_10050_wc$sd^2))/max(all_10050_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

### When the group effects change throughout the time

#### Group settings: 

+ 100 people, 4 groups with 25 people in every group. 

+ Baseline group effects (don't influence treatment effect estimation) follow **N(0,0.5)**, $b_gs$ follow **N(0,0.1)**, and $b_{g,2}s$ follow **N(0,1e-04)**.

+ T = 30 & 50

+ Y is generated as follows : 


$$
Y_{i(t+1)} = (-0.2 + b_g + b_{g,2} \times t + \beta_{11}^*S_{it}) \times (A_{it} -p_t(1|H_{it})) + 0.8 S_{it} + \text{group_err}_g +\text{err}_{it}
$$

#### Model

I constructed a model which looks like: 

$$
\text{y ~ state + I(a - pn)} 
$$

#### CP  

We tested whether the CI of the coefficient of $\text{I(a - pn)}$ covers $(-0.2 + b_g)$ or not in different groups. 


```{r echo=FALSE}
load("~/MRT/testing/test-bg2.RData")
all <- omit

all_10030_wc= subset(all, n ==100 & tmax == 30 & level == '$\\beta_{11}^* = 0.2$')

all_10030_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=100, T =30)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_10030_wc$estc)
sd =sqrt(sum(all_10030_wc$sd^2))/max(all_10030_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```


```{r echo=FALSE}
all_10030_wc= subset(all, n ==100 & tmax == 30 & level == '$\\beta_{11}^* = 0.5$')

all_10030_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=100, T =30)", align = "c") %>%
  kable_styling("striped")
```

```{r echo=FALSE}
point = mean(all_10030_wc$estc)
sd =sqrt(sum(all_10030_wc$sd^2))/max(all_10030_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_10030_wc= subset(all, n ==100 & tmax == 30 & level == '$\\beta_{11}^* = 0.8$')

all_10030_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=100, T =30)", align = "c") %>%
  kable_styling("striped")
```

```{r echo=FALSE}
point = mean(all_10030_wc$estc)
sd =sqrt(sum(all_10030_wc$sd^2))/max(all_10030_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_10050_wc= subset(all, n ==100 & tmax == 50 & level == '$\\beta_{11}^* = 0.2$')

all_10050_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=100, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_10050_wc$estc)
sd =sqrt(sum(all_10050_wc$sd^2))/max(all_10050_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_10050_wc= subset(all, n ==100 & tmax == 50 & level == '$\\beta_{11}^* = 0.5$')

all_10050_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=100, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_10050_wc$estc)
sd =sqrt(sum(all_10050_wc$sd^2))/max(all_10050_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```

```{r echo=FALSE}
all_10050_wc= subset(all, n ==100 & tmax == 50 & level == '$\\beta_{11}^* = 0.8$')

all_10050_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=100, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
point = mean(all_10050_wc$estc)
sd =sqrt(sum(all_10050_wc$sd^2))/max(all_10050_wc$group)
upper = point + 1.96 *sd
lower = point - 1.96* sd
cat("The estimation for treatment effect is",round(point, digits = 3), "\n")
cat("The 95% MC CI for treatment effect is (",lower,",", upper,")", "\n")
```
