---
title: "Estimate group treatment effect"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyr)
require(data.table)
require(kableExtra)
```

## Tables

### Group settings: 

+ 30 people, 6 groups with 5 people in every group. 

+ Baseline group effects (don't influence treatment effect estimation) follow **N(0,0.5)**, and group random treatment effects follow **N(0,0.1)**.

+ T = 30 & 50

+ Y is generated as follows : 


$$
Y_{i(t+1)} = (-0.2 + \text{group treatment diff}_i + \beta_{11}^*S_{it}) \times (A_{it} -p_t(1|H_{it})) + 0.8 S_{it} + \text{group_err}_i +\text{err}_{it}
$$

### Model

I constructed a model which looks like: 

$$
\text{y ~ state + I(a - pn)} 
$$

### CP  

We tested whether the CI of the coefficient of $\text{I(a - pn)}$ covers $(-0.2 + \text{group treatment diff}_i)$ or not in different groups. 


```{r echo=FALSE}
load("~/MRT/testing/test_groupeffect.RData")
all <- omit

all_3030_wc= subset(all, n ==30 & tmax == 30 & level == '$\\beta_{11}^* = 0.2$')

all_3030_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
all_3030_wc= subset(all, n ==30 & tmax == 30 & level == '$\\beta_{11}^* = 0.5$')

all_3030_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
all_3030_wc= subset(all, n ==30 & tmax == 30 & level == '$\\beta_{11}^* = 0.8$')

all_3030_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =30)", align = "c") %>%
  kable_styling("striped")
```






```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & level == '$\\beta_{11}^* = 0.2$')

all_3050_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & level == '$\\beta_{11}^* = 0.5$')

all_3050_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```


```{r echo=FALSE}
all_3050_wc= subset(all, n ==30 & tmax == 50 & level == '$\\beta_{11}^* = 0.8$')

all_3050_wc[,c("level","group","estc","sec","cpc","rmse","sd")] %>% 
  kable(caption = "Weighted and centered with group structure (n=30, T =50)", align = "c") %>%
  kable_styling("striped")
```
